\tool: Revisiting BadUSB with Type-C

### 2021-03-10 WOOT/Files/countermeasure.tex
Update

Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
proposed as countermeasures against BadUSB attacks. As mentioned in
Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
internal display for authorization, which can be bypassed via our \tool. 
%Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but
%no defense at all for our \tool. 
Next, we discuss our recommended countermeasures against \tool.

\textbf{External Hardware Authorization.} One possible countermeasure is to
introduce external hardware completing the authorization process. For example,
 \mbox{USBCheckIn}~\cite{usbcheckin} adopts a dedicated hardware between
the host and device. When a device is plugged-in, the authorization will be
conducted on the dedicated hardware instead of the internal display, preventing
the host from being hijacked. Though \mbox{USBCheckIn} is an adequate defense against
\tool, the external hardware brings additional cost and inconvenience,
especially for mobile devices.

@@

\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
is actually unable to redirect out the locking screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the locking screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated \ac{UI} Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
is secure the other is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive. Thus, the `password' and `keyboard' are not rendered on untrusted screen.

>>>>

%Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
%proposed as countermeasures against BadUSB attacks. As mentioned in
%Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
%internal display for authorization, which can be bypassed via our \tool. 
%Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but
%no defense at all for our \tool. 
Next, we discuss our recommended countermeasures against \tool.

\textbf{External Hardware Authorization.} One possible countermeasure is to
introduce external hardware completing the authorization process. For example,
 \mbox{USBCheckIn}~\cite{usbcheckin} adopts a dedicated hardware between
the host and device. When a device is plugged-in, the authorization will be
conducted on the dedicated hardware instead of the internal display, preventing
the host from being hijacked. Although \mbox{USBCheckIn} is an adequate defense against
\tool, the external hardware brings additional cost and inconvenience,
especially for mobile devices.

@@

\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
is actually unable to mirror the lock screen keyboard from the iPad
OS. Instead, the keyboard is only available on the internal display. However,
this defense is only enabled on the lock screen keyboard, other keyboards
(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
This mechanism has inspired us to propose a new defense against our \tool
called \emph{Isolated \ac{UI} Rendering}. As illustrated in
Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
is secure the other is insecure. When an application requires to render, it can
pass the content along with a tag identifying whether the content is
``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
will only render it on the secure layer, which only shows the sensitive content
(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
would render on both the trusted and untrusted display (e.g., insensitive
contents).
For example, in Figure~\ref{fig:isolated_ui}, the ``password'' and ``keyboard'' are recognized as sensitive while other parts of content are insensitive. Thus, the ``password'' and ``keyboard'' are not rendered on untrusted screen.

### 2021-03-10 WOOT/Files/discussion.tex
Update

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. Depending on victim's settings, the \tool may be used as an extended monitor or not be enabled at all. Additionally, some smartphone vendor (e.g. Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring. In these cases, \tool is either easily noticeable to victim or disabled.  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connector does not support \ac{USB} 3.2 protocol. This lack of support further limited \tool.
\begin{comment}
There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the \ac{USB} devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.
\end{comment}
\subsection{Impact}

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  Due to the neglect to
check the security of plugged-in \ac{USB} devices of non-professional users, \tool
can be hardly detected by them while attacks are performing.  The popularity
and universality of public \ac{USB} devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface, as well as control the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

>>>>

\subsection{Limitation}
There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all. Additionally, some smartphone vendors (e.g. Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring. In these cases, \tool is either easily noticeable to the victim or disabled.  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor. In iPad, there is a small blue icon on the notification bar. In Windows 10, there is a pop-up for user to select the functionality of the external monitor. In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements. But they are still noticeable by the victim. Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices. When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors do not support \ac{USB} 3.2 protocol. Such lack of support further limits \tool.
\begin{comment}
There exist multiple limitations of \tool.  To begin with, \tool can only gain
the information and control access of the host itself instead of external
hardware.  Consequently, as we introduced in the
Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
approaches that use external hardware for authorization.  Moreover, most of
the devices will prompt users to give authentication to the \ac{USB} devices or
select one of the functional modes after they are plugged in.  Though some of
such prompts are not conspicuous for non-experts, especially when \tool is
concealed within other functional hardware such as power banks \shuqing{If
there is experiment, add it here.}, the probability of whether users could get
aware that something unusual happens will increase with the existence of these
prompting messages.
\end{comment}
\subsection{Impact}

%\shuqing{Left after experiment to finish. Will discuss from different modes
%and application scenarios.}
The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
technologies develop rapidly, more and more devices will be equipped with USB-C
capabilities, which makes \tool more influential.  
Since non-professional users often neglect checking the security of plug-in \ac{USB} devices, they are often unaware of the attacks from \tool.
can be hardly detected by them while attacks are performing.  
The popularity and universality of public \ac{USB} devices, including sharing power banks, even
increase such risks.  Moreover, \tool provides a better way for traditional
BadUSB attacks, since attackers can obtain the screen streaming with ease.
Attackers can use such technologies to perform more precise attacks, such as
interacting with the user interface and controlling the consequences of their
attacks.  In summary, \tool can be applied in various application scenarios and
brings rather huge impacts.

### 2021-03-10 WOOT/Files/experiment.tex
Update

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
====================================================
As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  
When the victim viewed text or photos withnt is typically performed in the following steps:
====================================================
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

\begin{enumerate}[I. ]
	\item The attacker rents a power bank from one of the power bank stations and replaces the internal components with \tool.
	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
	\item A user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
\end{enumerate}

Next, we summarize the possible threats toward users under different modes.
%\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims accesses their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we discloses to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which is considered as a normal power bank usage time.
To obtain data close to real-life, they were requested to use phones just as they would when normally using the shared power banks.\shuqing{check}
After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. It protects their privacy and is also a mark for us to confirm that the data we find contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us. 
\shuqing{Do we need to mention that agreement the conference required here?}
\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data collected from 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expression are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

>>>>

\textbf{QR Code Payment}.
QR code payment is a new type of payment method that is popular in Asia. Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}. QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
As illustrated in Figure~\ref{fig:qr_payment_procedure},
 QR code payments are typically performed in the following steps:
\ding{182} The client presents the payment QR code on the mobile device to the merchant.
The QR code is encoded with a globally unique ID to identify the client's account.
\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
By presenting this QR code, the client authorizes the proceeding transaction.
\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
\hongyi{Dont know how to be more concise.}

@@

\begin{enumerate}[I. ]
	\item The attacker rents a power bank from one of the power bank stations and replaces the internal components with \tool.
	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
	\item A user borrows the modified power bank and connects it to his/her own device, becoming the victim of \tool.
	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
\end{enumerate}

Next, we summarize the possible threats toward users under different modes.
%\hongyi{Better way to express this?}
First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices. Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker. Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.

@@

To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
Before the user study experiment, we disclosed to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
During the case study, volunteers took turns to use their phones for half an hour with \tool connected.
To obtain data close to real-life, they were requested to use phones just as they were normally using sharing power banks.
After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks. This protects their privacy and is also a mark for us to confirm that the data we find contains their private data. At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us. 
%\shuqing{Do we need to mention that agreement the conference required here?}
%\hongyi{I'm also quite concern about this.}

@@

After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
In total, there are 94,058 entries of data from 10 volunteers.
%\shuqing{The data may need to be updated.}
With these results, we could learn what content the victim visited, especially the privacy data.
%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
The records searched by such keywords and regular expressions are usually related to privacy information of users.
For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
%\shuqing{Statistics.}
The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.

### 2021-03-10 WOOT/Files/related_work.tex
Update

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.

After the \ac{USB} enumeration and driver loading, some related works
archive `defense in depth'
against BadUSB attacks.  Neuner \emph{et al.}~\cite{neuner2018usblock}
prevent BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject keystrokes in a very
short time to reduce the risk of being discovered. This defect causes the
typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
a honeypot to detect and stop malicious behavior of \ac{USB} devices.

>>>>

To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
by the device to the user and let the user decide whether to authorize. When a device
is plugged in, GoodUSB limits its functionality before enumeration until a
series of authorizations are completed. These authorizations are designed to be
performed manually, thus the malicious devices will be detected if they make a different claim 
that does not match the authorization results. 
USBeSafe\cite{usbesafe} analyses the 
feature vector constructed with the data collected from \acp{URB}, 
detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
a alert to the user before enumeration. As BadUSB attacks normally request privileged 
interfaces during enumerating, these defenses are sufficient for these attacks.
Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience. It can detect the presence of the user, block malicious device in the user's absence until the session is unlocked.

After the \ac{USB} enumeration and driver loading, some related works follow the \textit{defense in depth} approach to defend against BadUSB attacks.  
Neuner \emph{et al.}~\cite{neuner2018usblock}
prevent BadUSB attacks from the malicious flash drive by analyzing
the temporal characteristics of BadUSB-like attacks. This defense mechanism is
effective because the attacker cannot obtain the screen of the host using
BadUSB. In this case, the malicious device can only inject keystrokes in a very
short time to reduce the risk of being discovered. This defect causes the
typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
block the execution of unsigned files and the installation of unsigned drivers
carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
a honeypot to detect and stop malicious behavior of \ac{USB} devices.
